\Large Bayes network classifiers for fRMI

### 2012-09-14 proposal/proposal.tex
small spelling
Added citation instead of footnote.

For our project, we are using a collection of data from the StarPlus project. This dataset contains the results from a trial experiment performed at Carnegie Mellon University. The data was originally collected by Marcel Just \textit{et al} \cite{StarPlus:2004kx}.

@@

The dataset we use originated from a project that researched classifying cognitive state using Gaussian Naive Bayes classifiers. This resulted in an accuracy of approximately 85\%. According to literature \cite{Friedman:1997gw}, a higher accuracy could be obtained by using a so-called \textit{Tree Augmented Naive Bayesian network classifier}, or TAN. We will use this classification method to investigate whether we are indeed able to reach a higher accuracy.

@@

Participants performed an experiment while laying in an fMRI scanner. The experiment consisted of sets of trials where participants were presented a first stimulus for four seconds, followed by a blank screen lasting four seconds, and then a second stimulus for four seconds, followed by a rest period of 15 seconds. For the first half of the trials, a picture was presented as the first stimulus and a sentence as the second stimulus, while for the second half of trials, a sentence was presented as the first stimulus and a picture as the second. Participants had four seconds after the second stimulus appeared to indicate that the sentence and picture belonged together, after which the stimulus disappeared. If participants did not press a button the stimulus would disappear after four seconds.

@@

In this section we describe the various phases and the planning deadlines that the group will follow.

\begin{description}
	\item[11th - 21st September]\-\\
	During this time period, the group members will conduct an initial research. The research will focus on the Bayes network classifiers and especially on the TAN tree algorithm.
	\item[22nd - 28th September]\-\\
	During this time period, the definition of the various models will be realised.
	\item[29th - 19th October]\-\\
	Implementation and Parameter estimation ...
	\item[20th - 22nd October]\-\\
	During this time period the group members will prepare the presentation of the project.
	\item[28th October]\-\\
	Until the aforementioned date the final version of the document and the implementation will be delivered.
\end{description}

>>>>

For our project, we are using a collection of data from the StarPlus project\footnote{StarPlus project - http://www.cs.cmu.edu/afs/cs.cmu.edu/project/theo-81/www/}. This dataset contains the results from a trial experiment performed at Carnegie Mellon University. The data was originally collected by Marcel Just \textit{et al}.

@@

The dataset we use originated from a project that researched classifying cognitive state using Gaussian Naive Bayes classifiers. This resulted in an accuracy of approximately 85\%. According to literature\cite{Friedman:1997gw}, a higher accuracy could be obtained by using a so-called \textit{Tree Augmented Naive Bayesian network classifier}, or TAN. We will use this classification method to investigate whether we are indeed able to reach a higher accuracy.

@@

Participants performed an experiment while laying in an fMRI scanner. The experiment consisted of sets of trials where participants were shown a first stimulus for four seconds, then a blank screen for another four seconds, and then a second stimulus for four seconds, which was followed by a rest period of 15 seconds. For the first half of the trials, a picture was used as first stimulus and a sentence was used as second stimulus, while the second half of trials showed a sentence as the first stimulus and a picture as the second. Participants had four seconds after the second stimulus appeared to indicate that the sentence and picture belonged together, after which the stimulus disappeared. If participants did not press a button the stimulus would disappear after four seconds.

@@

Describe the different phases and the planning deadlines (until November)

\begin{description}
	\item[11th - 21st September]\-\\
	During this time period, the group members will conduct an initial research. The research will focus on the Bayes network classifiers and especially on the TAN tree algorithm.
	\item[22nd - 28th September]\-\\
	During this time period, the definition of the model will be realised. \cite{CV:2009kl}
	\item[29th - 19th October]\-\\
	Implementation and Parameter estimation ...
	\item[20th - 22nd October]\-\\
	Preparing the presentation ...
	\item[28th October]\-\\
	Final delivery of the document and the implementation
\end{description}
